Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-01-25 Ben_Manuscripts/structure_paper/Draft.tex
draft updates

@@

  Current commercial RO and NF membranes suffer from limitations inherent to
  their fabrication. Although scalable, each of these two types of membranes has
  a degree of stochasticity that makes overcoming the permeability-selectivity
  tradeoff a challenge. Namely, it is difficult to increase the permeability of
  a desired molecular or atomic species, while maintaining the same retention of
  an undesired species \cite{werber_materials_2016}.

>>>>

  Reverse osmosis (RO) and nanofiltration (NF) are membrane based separation
  processes widely used to create potable or reusable water by removing salts and
  other dissolved compounds from water sources. RO membranes are typically thin
  film composite (TFC) membranes with a porous support layer and a dense
  crosslinked polymer active layer which near indiscriminately separates all solutes.
  NF membranes are porous with pores on the order of 1 $\nm$ in size which separate 
  primarily based on solute size.

  RO and NF are finding applications beyond primarily water-based
  separation. Recovery of valued products from complex aqueous and organic waste
  is of increasing interest. This requires highly selective membranes.

%  The permeability-selectivity tradeoff is a well-known problem in the membrane
%  separations community. It is difficult to increase the permeability of a 
%  desired molecular or atomic species, while maintaining the same retention of
%  an undesired species.

%  Current commercial RO and NF membranes suffer from limitations inherent to
%  their fabrication. Although scalable, each of these two types of membranes has
%  a degree of stochasticity that makes overcoming the permeability-selectivity
%  tradeoff a challenge. Namely, it is difficult to increase the permeability of
%  a desired molecular or atomic species, while maintaining the same retention of
%  an undesired species \cite{werber_materials_2016}.

  Selective separation by a semipermeable membrane barrier is governed by two
  steps : barrier entry and transport through the barrier. A solute's ability to
  enter a membrane barrier is decided by its size, solubility and charge. A solute's
  size, shape and polarity affect its ability to travel across the barrier. Undesired
  solutes may still be able to enter the membrane making their diffusion rates
  relative to desired solutes important. It is important to design the membrane in response
  to desired and undesired solutes is thus important.

  NF -- pore polydispersity
  RO -- r0andom walk through polymer voids

@@
